Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-03 MUSES_vs_BYOD_solutions.tex
More comments from Pedro, added to Android for Work section

On the device side, one of the most powerful solutions found in the BYOD state of the art seems to be to directly use a phone which has been developed with data security in mind such as the BlackPhone \cite{Blackphone}. It has its own Android-based operating system, called \textit{PrivatOS}, which includes a privacy-focused application store (called \textit{Silent Store}) that takes care of the problem of applications which ask for certain permissions that can lead, for instance, to personal data leakage \cite{gangula2013survey}. This BlackPhone also allows a remote wiping of the data if the device is lost or stolen. The main disadvantage of this solution is either the enterprise having to make
an investment and buy these smartphones to the employees (which, in fact, is against the BYOD philosophy), or to make employees buy them,
so they cannot use the device they already have. On the contrary, the MUSES system proposed in this work is designed as device-independent.

@@

Android work has only one advantage over MUSES, and roughly over all solutions, which is the ability to act over the Android kernel. All the other tools only have permission for monitoring the running processes in the devices, while Android work has, for instance, the ability to provide a `work' version of its native apps. MUSES, instead, depends on if the developers adapt their applications through a MUSES API, transforming them to MUSES Aware apps (see Section \ref{subsec:client}). In any other case, and most of all with the ``self-adaptation'' feature of MUSES, it can be said that MUSES has more advantages than the Google solution.

>>>>

On the device side, one of the most powerful solutions found in the BYOD state of the art is, apparently, to directly use a phone which has been developed with data security in mind such as the BlackPhone \cite{Blackphone}. It has its own Android-based operating system, called \textit{PrivatOS}, which includes a privacy-focused application store (called \textit{Silent Store}) that takes care of the problem of applications which ask for certain permissions that can lead, for instance, to personal data leakage \cite{gangula2013survey}. BlackPhone also allows a remote wiping of the data if the device is lost or stolen. The main disadvantage of this solution is either the enterprise having to make
an investment and buy these smartphones to the employees (which, in fact, is against the BYOD philosophy), or to make employees buy them,
so they cannot use the device they already have. On the contrary, the MUSES system proposed in this work is designed as device-independent.

@@

Android Work presents only one advantage over MUSES, and roughly over all solutions, which is the ability to act over the Android kernel. The rest of tools only have permission for monitoring the running processes in the devices, while Android Work has, for instance, the ability to provide a `work' version of its native apps. MUSES, instead, depends on the developers to adapt their applications through a MUSES API, transforming them to MUSES Aware apps (see Section \ref{subsec:client}). In any other case, and most of all with the ``self-adaptation'' feature of MUSES, it can be said that MUSES presents more advantages than the Google solution.
